A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 1_intro.tex
Updates from Overleaf

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width. 
This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where a wide range of widths could be realized by the hardware. 
For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.
However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (the preferred width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate. 
Therefore, a much narrower range of widths is desirable for robust FDM fabrication.
On the other hand, controlling the variation in width is beneficial for limiting the variation in mechanical properties of the resulting material fragments. 
% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.

>>>>

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width. 
This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where it has been shown that a wide range of widths could be realized by the hardware. 
For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.
However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (the preferred width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate. 
Therefore, a much narrower range of widths is desirable for robust FDM fabrication.
On the other hand, controlling the variation in width is beneficial for limiting the variation in mechanical properties of the resulting material fragments. 
% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.

### 2019-08-30 2_related_work.tex
Updates from Overleaf

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged.
The variation of width in the central is pronounced (\cref{intro_wedge} middle).
In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).

>>>>

% the idea, and (some of) the most related work
Our approach to reduce under- and over-filling is to deposit material with a varying width.
This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
However, we note that the range of possible widths is not unlimited.
For instance, printing a width that is triple the nozzle diameter is challenging.
Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.
An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
This extension, however, inherits a problem in the original method.
From any point in the geometry skeleton to the boundary, the number of contours is constant.
Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
The resulting variation of width in the central is pronounced (\cref{intro_wedge} middle).
In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).
